When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added Hxx confirmations

The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

@@

All NASA-TLX subscale scores increased across $n$-back levels.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

@@

The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.

@@

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.

@@

The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

>>>>

We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across $n$-back levels.
The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), evidence was not in favour of H1a but in favour of H1b.
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

@@

All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

@@

The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`), so evidence was in favour of H2a.
All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.

@@

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
Since SVs decline with increasing level, beyond the variance explained by $d'$, evidence was in favour of H2b.

@@

The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.
